---
output: 
  github_document:
    toc: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the ggtedious workshop!

<!-- badges: start -->
<!-- badges: end -->

Let's build a vanilla ggplot2 Stat and use it in an extension function.  

# Part 1. Work on functionality

## Step 0. Do it with base ggplot2 *can become problem statement later*

```{r use_base_ggplot2}
library(tidyverse)

cars_means_df <- cars |>
  summarise(dist = mean(dist),
            speed = mean(speed))

ggplot(data = cars) + 
  aes(speed, dist) + 
  geom_point() + 
  geom_point(data = cars_means_df, size = 8)
```

## Step 0.b Write like-to-have code *code chunk option eval = F*

```
ggplot(data = cars) + 
  aes(speed, dist) + 
  geom_point() + 
  geom_pointmeans(size = 8)
```


## Step 1. Write compute group function and test

## Step 2. Pass to ggproto object

reference: https://evamaerey.github.io/mytidytuesday/2022-01-03-easy-geom-recipes/easy_geom_recipes.html

```{r compute_group_means}
compute_group_means <- function(data, scales){
  
  data |>
    summarise(x = mean(x),
              y = mean(y))
  
}


StatMeans <- ggproto(`_class` = "StatMeans",
                     `_inherit` = Stat,
                     compute_group = compute_group_means,
                     required_aes = c("x", "y"))


```

```{r try_compute_group_post}
cars |>
  select(x = speed, y = dist) |>
  compute_group_means()
```

```{r}
ggplot(data = cars) + 
  aes(speed, dist) + 
  geom_point() + 
  layer(stat = StatMeans, 
        geom = GeomPoint, 
        position = "identity",
        params = list(size = 8)) 

# defining params is not always required.
# we just use it hear so that our means point is obvious
```


## Step 3. Write user-facing geom_pointmeans() function

```{r geom_post}
geom_pointmeans <- function(mapping = NULL, 
                            data = NULL,
                            position = "identity", 
                            na.rm = FALSE,
                            show.legend = NA,
                            inherit.aes = TRUE, ...) {
  ggplot2::layer(
    stat = StatMeans,        # proto object from step 2
    geom = ggplot2::GeomPoint,   # inherit other behavior
    data = data, 
    mapping = mapping,
    position = position, 
    show.legend = show.legend, 
    inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}

```


## Step 4. Test it out enjoy! (possibly basis of examples and tests)

```{r}
ggplot(data = cars) + 
  aes(speed, dist) + 
  geom_point() + 
  geom_pointmeans(size = 8)

last_plot() + 
  aes(color = dist > 50)
```

## Step 5. Write messages/warnings etc in the function

# Part II. Packaging and documentation  🚧 ✅

## Phase 1. Minimal working package

### Bit A. Created package archetecture, running `devtools::create(".")` in interactive session. 🚧 ✅


```{r, eval = F}
devtools::create(".")
```

### Bit B. Added roxygen skeleton? 🚧 ✅

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported*.  Generally, early on, I don't do much (anything) in terms of filling in the skeleton for documentation, because things may change.

### Bit C. Managed dependencies ? 🚧 ✅

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r, eval = F}
usethis::use_package("ggplot2")
```


### Bit D. Moved functions R folder? 🚧 ✅

Use new {readme2pkg} function to do this from readme...

```{r, eval = F}
library(tidyverse)
readme2pkg::chunk_to_r("geom_post")
```

### Bit E. Run `devtools::check()` and addressed errors. 🚧 ✅

```{r, eval = F}
devtools::check(pkg = ".")
```

### Bit F. Build package 🚧 ✅

```{r, eval = F}
devtools::build()
```


### Bit G. Write traditional README that uses built package (also serves as a test of build. 🚧 ✅

The goal of the {ggtedious} package is to make it easy to draw posts (and to learn about package building and testing)

Install package with:

```
remotes::install_github("EvaMaeRey/ggvanilla")
```

Once functions are exported you can remove go to two colons, and when things are are really finalized, then go without colons (and rearrange your readme...)

```{r, eval = F}
library(ggvanilla)  


```




### Bit H. Chosen a license? 🚧 ✅


```{r, eval = F}
usethis::use_mit_license()
```

### Bit I. Add lifecycle badge (experimental) 🚧 ✅

```{r, eval = F}
usethis::use_lifecycle_badge("experimental")
```


## Phase 2: Listen & iterate 🚧 ✅

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let things settle

### Bit A. Settle on examples.  Put them in the roxygen skeleton and readme. 🚧 ✅

### Bit B. Written formal tests of functions and save to test that folders 🚧 ✅


That would look like this...

```{r test_calc_times_two_works, eval = F}
library(testthat)

test_that("calc times 2 works", {
  expect_equal(times_two(4), 8)
  expect_equal(times_two(5), 10)
  
})
```


```{r, eval = F}
readme2pkg::chunk_to_tests_testthat("test_calc_times_two_works")
```


### Bit C. Added a description and author information in the DESCRIPTION file 🚧 ✅

### Bit D. Addressed *all* notes, warnings and errors. 🚧 

## Phase 4. Promote to wider audience...

### Bit A. Package website built?  ✅

```{r, eval = F}
usethis::use_pkgdown()
pkgdown::build_site()
```


### Bit B. Package website deployed? 🚧 ✅

## Phase 5: Harden/commit

### Submit to CRAN/RUniverse? 🚧 

# Appendix: Reports, Environment

## Edited Description file?

```{r, eval = F}
readLines("DESCRIPTION")
```

